---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}

```

## Data summarising meals made by flatmates

I recorded the meals made by flatmates over multiple days.
The data recorded includes:

* What time of day the meals were made
* Which flatmates made the meals
* How many vegetables were included in said meals
* What cooking appliances were used for the meals
* how appealing the meals were
* if a recipe was used or not.

```{r}



#read csv and rename question data accordingly
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRVqfjnKAUWI1iT1YIqdaNRSAdqeAqdLRyQ_qwa2SMmcIjCyxhQmP4LMAf1-P1d9a5wB4WZmLO3B9KU/pub?output=csv")

#rename columns ( rename function didnt work with github so am trying this)
colnames(logged_data) <- c(
  "timestamp",
  "flatmate_id",
  "time_frame",
  "veg_quantity",
  "cooking_method",
  "appeal",
  "Recipe"
)

#Find the mean and max value for vegetables used.
mean_var_veg <- mean(logged_data$veg_quantity, na.rm = TRUE)
max_var_veg  <- max(logged_data$veg_quantity, na.rm = TRUE)

#find the mean value of the appeal of the meals
mean_var_appeal <- mean(logged_data$appeal, na.rm = TRUE)

```

The mean number of vegetables used throughout all recorded meals is  `r mean_var_veg` 
and the highest recorded vegetable sighting is `r max_var_veg` .

The average (Mean) appeal of all recorded meals is `r mean_var_appeal` .



The following Bar chart displays how often each cooking appliance was used for the recorded meals.
As shown, it was most common for no heating appliance to be used at all.
and the least commonly used appliance was the oven

```{r}
#bar chart for cooking implementation
logged_data %>%
  ggplot() +
  geom_bar(aes(x = cooking_method)) +
  labs(title = "Flatmates Cooking judgement",
       subtitle = "Comparing how often different cooking appliances were used by flatmates.",
       caption = "Source: My personal observation of flatmates",
       x = "Appliance",
       y = "Number of Uses")
```




The following bar chart shows how often flatmates were seen making meals.
as shown in the chart, the amount of meals made in the midday and evening was even. however the amount of meals made in the morning fell behind.

```{r}
#bar chart for Time Frame
logged_data %>%
  ggplot() +
  geom_bar(aes(x = time_frame)) +
  labs(title = "Comparison of what times meals were made",
       subtitle = "Comparing how often flatmates made meals at specific times of day",
       caption = "Source: My personal observation of flatmates",
       x = "Time of day",
       y = "number of meals")
```

